Probability of causal contact between interstellar civilizations through MonteCarlo simulations

### 2019-12-24 captions.tex
detalles de los captions

%_______________________________________________________________
\definecaption{F_scheme}{%
%
Space--time diagrams showing a schematic representation of the
different stages in the development of a communicating civilization,
the growing communicating sphere (a) and the temporal intervals for
the communication between two civilizations (b).
%
In the upper panel (a), the sphere the encloses the region which is
causally connected to the emitter grows until it reaches the
$D_{max}$ distance.  After the $D$ event, that region is limited by
the surface of last contact.
%
The scheme in the lower panel (b) represents two communicating
civilizations that have causal contact in both directions
%
}

%_______________________________________________________________
\definecaption{F_messages}{%
%   
Schematic representation of the possible cases in which a
ceti A can be in causal contact with a ceti B which appears later.
%   
The duration of the causal contact in one direction depends on
several factors, mainly $\Delta t_A$, $\Delta t_C$, and $\Delta X$.
%   
}

%_______________________________________________________________
\definecaption{F_number_of_contacts}{%
%
Empirical cumulative distributions of the number contacts
for MPLs in four different samples (M5, M6, M7, M8) with long
range signal reach (D$_{max}$=10000).
%
}

>>>>

%_______________________________________________________________
\definecaption{F_scheme}{%
%
Space--time diagrams showing a schematic representation of the
different stages in the development of a communicating civilization,
or causal contact node (CCN).
%
Panel (a) shows the sphere of first contact (SFC) centered on an A type
event and the surface of last contact (SLC), centered on a D type
event.
%
In the upper panel, the sphere that encloses the region which is
causally connected to the emitter grows until it reaches the
$D_{max}$ distance.  After the $D$ event, that region is limited by
the surface of last contact.
%
The temporal intervals for
the communication between two civilizations are represented in he
panel (b).
%
The receiver CCN E$_1$ can listen signals from the emiter CCN E$_2$,
from the contact event (C$_{12}$) up to the blackout event (B$_{12}$).
%
Similarly, 
the receiver CCN E$_2$ can listen signals from the emiter CCN E$_1$,
from C$_{21}$ up to B$_{21}$. 
%
The scheme in the lower panel (b) represents two communicating
civilizations that have causal contact in both directions
%
}

%_______________________________________________________________
\definecaption{F_messages}{%
%   
Schematic representation on space--time diagrams of the possible cases in which a
\ceti E (Emiter, solid line) can be in causal contact with a \ceti R
(Receiver, dashed line).
%
Causal contact can be produced either if the emiter \ceti appears before
(left) or after (right) the receiver \ceti.
%
The causal contact in which the receiver can have access to the signal 
from the emiter is produced between the C event (Contact, open circles) and the B
event (Blackout, filled circles).
%
The duration of the causal contact in one direction depends on
several factors, mainly the time lag between the awakening events
(horizontal separation in the space--time diagrams)
and the distance between the \cetis (vertical separation in the
space--time diagrams).
%   
The different configurations must be taken into account in order to 
obtain the list of the upcomming events.
%
The time intervals for a two--way communication to be possible are
indicated in double lines.
}

%_______________________________________________________________
\definecaption{F_number_of_contacts}{%
%
Empirical cumulative distributions of the number contacts
for \cetis in four different samples (M5, M6, M7, M8) with two
values for the range of the signal reach: D$_{max}$=40000 ly (blue),  and 
D$_{max}$=80000 ly (orange).
%
Except for the models corresponding to a densely populated galaxy with
long--living \cetis, the \cetis which receive more than 10 contacts
are very unlikely.
%
See Table \ref{T_selected_models} for model descriptions.
%
}

### 2019-12-24 manuscript.tex
detalles de los captions

\JELclassification{XX; XX}
\MSCcodes{XX; XX}

\Abbreviations{MPL: Communicating Extraterrestrial Intelligence, DE:
Discrete Event, GHZ: Galactic Habitable Zone}

@@

>>>>

%\JELclassification{XX; XX}
%\MSCcodes{XX; XX}

\Abbreviations{SETI: Search for Extraterrestrial Intelligence,\\
CCN: causally connected node,\\
SFC: surface of first contact,\\
SLC: surface of last contact,\\
DE: Discrete Event,\\
GHZ: Galactic Habitable Zone}

@@

M essage
P rocessing
L ocation
E mission
R eceiver
E xtraterrestrial
I ntelligence
E xposed
B roadcasting
T ransmission
R eveal
S ource
D eliver
W hisper
A gent
N etwork
C ausal
C ontact
I nterstellar
E ntity
W atch
O utlook  (the place from which an observer looks out)
L ookout  (a station or place from which a watch is kept)
A wakening (a recognition, realization, or coming into awareness of something)

CETI communicating extraterrestrial intelligence
MPL message processing location
ELI   Exposed Lookout Intelligence
EWI   Exposed Watching Intelligence
EBIL  exposed Broadcasting Intelligent lookout
EBIO  exposed Broadcasting Intelligent outlook
ISBL  Intelligent station for broadcasting and lookout
BAOS  Intelligent station for broadcasting and outlook
EBI   exposed broadcasting intelligence
OSIRIS outlook station for intelligent reception of interstellar signals
SIS    Source of intelligent signals
SLSCC source of light speed causal contact
NLCC node for lightspeec causal contact
CCN causal contact nodes

awakening event:
Awakening Active Activation Broadcast

contact event:
Contact Communication Connect Acquaintance Bond Link

blackout event:
Blackout Disconnect Detach Cutoff  Obscure Veil Silence Mask

doomsday event:
Doomsday  Disappear Extinction

Emmit:

Receive:
catch, seize, hear,
